---
title: "Difference Function for NDVI and 2015 FAM"
author: "Elmera Azadpour"
date: "11/9/2021"
output: html_document
---

## raster to tif before we can do difference function
```{r}
library(sf)
library(fasterize)
library(raster)
library(tidyverse)
library(rgdal)

# read in (or create) raster with resolution, extent, crs, etc. that you want
template <- raster("Annual2015_geotiff_13Oct20151.tif") # filepath to template raster


# read in polygon and make sure its in same projection
polygon_fallow <- st_read(dsn = "maxNDVIJun_kern2015_fallow", # folder shapefile is in
                   layer = "polygons_kern_maxNDVIJun_Fallow") %>%  # name of files - i.e., I have 'AltoMayo.dbf', 'AltoMayo.shp', etc.
  st_transform(crs = crs(template)) # make sure its in the same projection as the template

# convert to raster with fasterize
raster_fallow <- fasterize(
  sf = polygon_fallow,
  raster = template
)

# save raster as .tif
#writeRaster(x = raster_fallow, filename = "polygons_kern_maxNDVIJun_Fallow.tif")



## Same idea but for ag shp
# read in polygon and make sure its in same projection
polygon_ag <- st_read(dsn = "maxNDVIJun_kern2015_ag", # folder shapefile is in
                   layer = "polygons_kern_maxNDVIJun_Agriculture") %>%  
  st_transform(crs = crs(template)) # make sure its in the same projection as the template

# convert to raster with fasterize
raster_ag <- fasterize(
  sf = polygon_ag,
  raster = template
)

writeRaster(x = raster_ag, filename = "polygons_kern_maxNDVIJun_Agriculture.tif")


## apply a subtract function 
Annual2015 <- raster("Annual2015_, 90-geotiff_13Oct20151.tif")
Kern_maxNDVIJun_Ag <- raster("polygons_kern_maxNDVIJun_Agriculture.tif")
Kern_maxNDVIJun_Fallow <- raster("polygons_kern_maxNDVIJun_Fallow.tif")

## apply a difference between annual 2016 and new ndvi ag classifcation 
outputRaster <- overlay(Annual2015, Kern_maxNDVIJun_Ag, fun=diff)
outputRaster_fallow <- overlay(Annual2015, Kern_maxNDVIJun_Fallow, fun=diff)
# writeRaster(x = outputRaster, filename = "diff_annual2015_kernmaxNDVIjun.tif") # doesn't work 
# writeRaster(x = outputRaster_fallow, filename = "diff_annual2015_kernmaxNDVIjun_fallow.tif") # doesn't work 
```


## Patrick's code help for doing the difference function
```{r}
# For Fam data 1 = Fallow; 2 = Ag
library(raster)

 ### need to designate this somewhere so you can find the temp files raster will write
rasterOptions(tmpdir="~/Desktop/ArnholdFellow-Su21/Histogram_StartDates/kern_histogram/kern_histogram/temp_tif")

fam <- raster("~/Desktop/ArnholdFellow-Su21/Histogram_StartDates/kern_histogram/kern_histogram/difference/Annual2015_geotiff_13Oct20151_INT2U.tif")
fallow <- raster("~/Desktop/ArnholdFellow-Su21/Histogram_StartDates/kern_histogram/kern_histogram/difference/polygons_kern_maxNDVIJun_Fallow.tif")
ag <- raster("~/Desktop/ArnholdFellow-Su21/Histogram_StartDates/kern_histogram/kern_histogram/difference/polygons_kern_maxNDVIJun_Agriculture.tif")

### remove the '1' (Ag) category from FAM
fam[fam==2]<-0

### convert fallow in FAM to values of 2
fam[fam==1]<-2 

### make a stack of the two rasters
s <- stack(fam,fallow)


### sum them (need the na.rm=TRUE argument to ignore NA values)
s_sum <- calc(s, sum, na.rm=TRUE)

### limit all this to areas you actually analyzed so can make a mask that combines your ag + fallow:
mask_stack <- stack(ag,fallow)
mask <- calc(mask_stack,sum,na.rm=TRUE)
mask[mask==0]<- NA

### will limit values to your analytical domain
s_sum_mask <- mask(s_sum, mask)
# writeRaster(x = s_sum_mask, filename = "diff_FAM_kernmaxNDVIjun_2015.tif") # export this
# plot(s_sum_mask)

## tabulate the values for each category for performance statistics
freq(s_sum_mask) 
```


```{r}
maxmean <- raster("~/Desktop/ArnholdFellow-Su21/Histogram_StartDates/kern_histogram/kern_histogram/difference/polygons_kern_maxmeanNDVIJun_2015.tif")
plot(maxmean)
```

### New approach to difference function, excluding geo column and looking at classifcation and system index features only 
## read in packages
```{r}
library(tidyverse)
library(here)
library(janitor)
```

## read in excel sheet with FAM ag and fallowed classifcation and then our NDVI classification
```{r}
FAM_fc_kern <- read_csv(here("data", "FAM_fc_Kern.csv")) %>% 
  clean_names() %>% 
  rename(classification = median) %>% 
  select(system_index, pmt_site, classification)

landsat8_ndvi_kern2015<- read_csv(here("data", "landsat8_ndvi_series_kern.csv")) %>% 
  clean_names() %>% 
  select(system_index, matching_kern_polygon_id, pmt_site, max_ndvi, classification) %>% 
  mutate(
 classification = case_when(
     classification== 0 ~ 2, ## convert 0 to 2 to match fallow classifcation binary across both classific.
    TRUE ~ classification
 ))
```

## merge dataframes by "pmt_site"
```{r}
## merge FAM and our classification
merged_df <- right_join(FAM_fc_kern, landsat8_ndvi_kern2015, by = "pmt_site")

## count matching/not
merged_df_matching <- merged_df %>% mutate(matching = 
                                             ifelse(classification.x==classification.y,"Yes","No"))

## now filter the non matching 
merged_df_nonmatching <- merged_df_matching %>% 
  filter(matching == "No") 

## now filter the matching 
merged_df_matchingonly <- merged_df_matching %>% 
  filter(matching == "Yes") 

```

