---
title: "Kern County Dates Active/Inactive Histograms & Renaming organic croplands"
author: "Elmera Azadpour"
date: "8/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
library(sf)
library(stringr)
```

### Read in Data
```{r}
# Note: Comm_code = 66000 is  fields that were cultivated then fallowed, but only available for 2017-2019
kern_2011 <- read_sf(here("kern2011"), layer = "kern2011") %>% 
  clean_names() %>% 
  select(dt_act,dt_inact)

kern_2014 <- read_sf(here("kern2014"), layer = "kern2014") %>% 
  clean_names()

kern_2015 <- read_sf(here("kern2015"), layer = "kern2015") %>% 
  clean_names() %>% 
  select(dt_act,dt_inact)

kern_2016 <- read_sf(here("kern2016"), layer = "kern2016") %>% 
  clean_names() 

kern_2017 <- read_sf(here("kern2017"), layer = "kern2017") %>% 
  clean_names() 

kern_2018 <- read_sf(here("kern2018"), layer = "kern2018") %>% 
  clean_names() 

kern_2019 <- read_sf(here("kern2019"), layer = "kern2019") %>% 
  clean_names() 
```

### Histogram of start and end dates, 2015
```{r}
# 2015 active
ggplot(kern_2015, aes(x= dt_act)) + 
  geom_histogram(bins=20) +
  scale_x_date(date_breaks = "1 month") +
   theme(axis.text.x = element_text(face="bold", angle=90))+
  ggtitle("Date active, 2015")
# 2015 inactive
ggplot(kern_2015, aes(x= dt_inact)) + 
  geom_histogram(bins=20)+
  scale_x_date(date_breaks = "1 month") +
   theme(axis.text.x = element_text(face="bold", angle=90))+
  ggtitle("Date inactive, 2015")
```


### Histogram of start and end dates, 2011
```{r}
# 2015 active
ggplot(kern_2011, aes(x= dt_act)) + 
  geom_histogram(bins=20) +
  scale_x_date(date_breaks = "1 month") +
   theme(axis.text.x = element_text(face="bold", angle=90)) +
  ggtitle("Date active, 2011")
# 2015 inactive
ggplot(kern_2011, aes(x= dt_inact)) + 
  geom_histogram(bins=20)+
  scale_x_date(date_breaks = "1 month") +
   theme(axis.text.x = element_text(face="bold", angle=90))+
  ggtitle("Date inactive, 2011")
```


### Lets add a column to the data frame that indicates 66000 = fallowed and non & add a column that gives orgnaic cropland them a new comm code: https://docs.google.com/spreadsheets/d/159WnaY9ubksf3o1NNounLtWanzmQ38TjbSaKNHXFyB0/edit?usp=sharing 
```{r}
kern_2017$comm_code <-  as.numeric(kern_2017$comm_code ) 

kern_2017 <- read_sf(here("kern2017"), layer = "kern2017") %>% 
  clean_names()%>% 
   mutate(landuse = case_when(comm_code == 66000 ~ 'fallow',
                             TRUE ~ 'cropland')) %>% 
   mutate(new_comm_code = case_when(str_detect(comm, "ALMOND-ORGANIC") ~ 30012,
                                    str_detect(comm, "APPLE-ORGANIC") ~ 40012,
                                    str_detect(comm, "APRICOT-ORGANIC") ~ 40012,
                                    str_detect(comm, "ARUGULA-ORGANIC") ~ 130562,
                                    str_detect(comm, "BEAN SUCCULENT-ORGANIC") ~ 150032,
                                    str_detect(comm, "BEET-ORGANIC") ~ 291092,
                                    str_detect(comm, "BLUEBERRY-ORGAN") ~ 10092,
                                    str_detect(comm, "BROCCOLI-ORGANI") ~ 130052,
                                    str_detect(comm, "CABBAGE-ORGANIC") ~ 130072,
                                    str_detect(comm, "CARROT-ORGANIC") ~ 291112,
                                    str_detect(comm, "CAULIFLOWER-ORGANIC") ~ 130082,
                                    str_detect(comm, "CHERRY-ORGANIC") ~ 50022,
                                    str_detect(comm, "CILANTRO-ORGANI") ~ 135012,
                                    str_detect(comm, "COLLARD-ORGANIC") ~ 130092,
                                    str_detect(comm, "CORN, HUMAN CON-ORGANIC") ~ 291192,
                                    str_detect(comm, "CUCUMBER-ORGANI") ~ 100102,
                                    str_detect(comm, "DILL-ORGANIC") ~ 80152,
                                    str_detect(comm, "EGGPLANT-ORGANI") ~ 110012,
                                    str_detect(comm, "FENNEL-ORGANIC") ~ 280082,
                                    str_detect(comm, "GARLIC-ORGANIC") ~ 140072,
                                    str_detect(comm, "GRAPE-ORGANIC") ~ 291412,
                                    str_detect(comm, "GRAPE, WINE-ORGANIC") ~ 291432,
                                    str_detect(comm, "GRAPEFRUIT-ORGANIC") ~ 20022,
                                    str_detect(comm, "KALE-ORGANIC") ~ 130112,
                                    str_detect(comm, "KOHLRABI-ORGANI") ~ 130122,
                                    str_detect(comm, "CHERRY-ORGANIC") ~ 50022,
                                    str_detect(comm, "LEMON-ORGANIC") ~ 20042,
                                    str_detect(comm, "LETTUCE HEAD-ORGANIC") ~ 130452,
                                    str_detect(comm, "MELON-ORGANIC") ~ 291222,
                                    str_detect(comm, "MINT-ORGANIC") ~ 280122,
                                    str_detect(comm, "OAT-ORGANIC") ~ 291252,
                                    str_detect(comm, "OKRA-ORGANIC") ~ 150152,
                                    str_detect(comm, "ONION DRY ETC-ORGANIC") ~ 140112,
                                    str_detect(comm, "ORANGE-ORGANIC") ~ 20062,
                                    str_detect(comm, "PARSLEY-ORGANIC") ~ 130222,
                                    str_detect(comm, "PEAS-ORGANIC") ~ 291272,
                                    str_detect(comm, "PEPPER FRUITNG-ORGANIC") ~ 110032,
                                    str_detect(comm, "PEPPER SPICE-ORGANIC") ~ 80502,
                                    str_detect(comm, "PERSIMMON-ORGANIC") ~ 60122,
                                    str_detect(comm, "POMEGRANATE-ORGANIC") ~ 60152,
                                    str_detect(comm, "POTATO-ORGANIC") ~ 140132,
                                    str_detect(comm, "RADISH-ORGANIC") ~ 140142,
                                    str_detect(comm, "SAFFLOWER-ORGANIC") ~ 291292,
                                    str_detect(comm, "SPINACH-ORGANIC") ~ 130242,
                                    str_detect(comm, "SQUASH-ORGANIC") ~ 100122,
                                    str_detect(comm, "SQUASH, WINTER-ORGANIC") ~ 100142,
                                    str_detect(comm, "SWISS CHARD-ORGANIC") ~ 130252,
                                    str_detect(comm, "TANGELO-ORGANIC") ~ 20072,
                                    str_detect(comm, "TANGERINE-ORGANIC") ~ 20082,
                                    str_detect(comm, "TANGERINE-ORGAN") ~ 20082,
                                    str_detect(comm, "TOMATO PROCESS-ORGANIC") ~ 291362,
                                    str_detect(comm, "TOMATO-ORGANIC") ~ 110052,
                                    str_detect(comm, "TURNIP-ORGANIC") ~ 291372,
                                    str_detect(comm, "UNCULTIVATED AG - ORGANIC") ~ 660002,
                                    str_detect(comm, "WATERMELON-ORGANIC") ~ 100082,
                                    str_detect(comm, "WHEAT-ORGANIC") ~ 291392
                                    ))

kern_2017$new_comm_code[is.na(kern_2017$new_comm_code)] <- kern_2017$comm_code[is.na(kern_2017$new_comm_code)]

kern_2018 <- read_sf(here("kern2018"), layer = "kern2018") %>% 
clean_names()  %>% 
   mutate(landuse = case_when(comm_code == 66000 ~ 'fallow',
                             TRUE ~ 'cropland')) %>% 
   mutate(new_comm_code = case_when(str_detect(comm, "ALMOND-ORGANIC") ~ 30012,
                                    str_detect(comm, "APPLE-ORGANIC") ~ 40012,
                                    str_detect(comm, "APRICOT-ORGANIC") ~ 40012,
                                    str_detect(comm, "ARUGULA-ORGANIC") ~ 130562,
                                    str_detect(comm, "BEAN SUCCULENT-ORGANIC") ~ 150032,
                                    str_detect(comm, "BEET-ORGANIC") ~ 291092,
                                    str_detect(comm, "BLUEBERRY-ORGAN") ~ 10092,
                                    str_detect(comm, "BROCCOLI-ORGANI") ~ 130052,
                                    str_detect(comm, "CABBAGE-ORGANIC") ~ 130072,
                                    str_detect(comm, "CARROT-ORGANIC") ~ 291112,
                                    str_detect(comm, "CAULIFLOWER-ORGANIC") ~ 130082,
                                    str_detect(comm, "CHERRY-ORGANIC") ~ 50022,
                                    str_detect(comm, "CILANTRO-ORGANI") ~ 135012,
                                    str_detect(comm, "COLLARD-ORGANIC") ~ 130092,
                                    str_detect(comm, "CORN, HUMAN CON-ORGANIC") ~ 291192,
                                    str_detect(comm, "CUCUMBER-ORGANI") ~ 100102,
                                    str_detect(comm, "DILL-ORGANIC") ~ 80152,
                                    str_detect(comm, "EGGPLANT-ORGANI") ~ 110012,
                                    str_detect(comm, "FENNEL-ORGANIC") ~ 280082,
                                    str_detect(comm, "GARLIC-ORGANIC") ~ 140072,
                                    str_detect(comm, "GRAPE-ORGANIC") ~ 291412,
                                    str_detect(comm, "GRAPE, WINE-ORGANIC") ~ 291432,
                                    str_detect(comm, "GRAPEFRUIT-ORGANIC") ~ 20022,
                                    str_detect(comm, "KALE-ORGANIC") ~ 130112,
                                    str_detect(comm, "KOHLRABI-ORGANI") ~ 130122,
                                    str_detect(comm, "CHERRY-ORGANIC") ~ 50022,
                                    str_detect(comm, "LEMON-ORGANIC") ~ 20042,
                                    str_detect(comm, "LETTUCE HEAD-ORGANIC") ~ 130452,
                                    str_detect(comm, "MELON-ORGANIC") ~ 291222,
                                    str_detect(comm, "MINT-ORGANIC") ~ 280122,
                                    str_detect(comm, "OAT-ORGANIC") ~ 291252,
                                    str_detect(comm, "OKRA-ORGANIC") ~ 150152,
                                    str_detect(comm, "ONION DRY ETC-ORGANIC") ~ 140112,
                                    str_detect(comm, "ORANGE-ORGANIC") ~ 20062,
                                    str_detect(comm, "PARSLEY-ORGANIC") ~ 130222,
                                    str_detect(comm, "PEAS-ORGANIC") ~ 291272,
                                    str_detect(comm, "PEPPER FRUITNG-ORGANIC") ~ 110032,
                                    str_detect(comm, "PEPPER SPICE-ORGANIC") ~ 80502,
                                    str_detect(comm, "PERSIMMON-ORGANIC") ~ 60122,
                                    str_detect(comm, "POMEGRANATE-ORGANIC") ~ 60152,
                                    str_detect(comm, "POTATO-ORGANIC") ~ 140132,
                                    str_detect(comm, "RADISH-ORGANIC") ~ 140142,
                                    str_detect(comm, "SAFFLOWER-ORGANIC") ~ 291292,
                                    str_detect(comm, "SPINACH-ORGANIC") ~ 130242,
                                    str_detect(comm, "SQUASH-ORGANIC") ~ 100122,
                                    str_detect(comm, "SQUASH, WINTER-ORGANIC") ~ 100142,
                                    str_detect(comm, "SWISS CHARD-ORGANIC") ~ 130252,
                                    str_detect(comm, "TANGELO-ORGANIC") ~ 20072,
                                    str_detect(comm, "TANGERINE-ORGANIC") ~ 20082,
                                    str_detect(comm, "TOMATO PROCESS-ORGANIC") ~ 291362,
                                    str_detect(comm, "TOMATO-ORGANIC") ~ 110052,
                                    str_detect(comm, "TURNIP-ORGANIC") ~ 291372,
                                    str_detect(comm, "UNCULTIVATED AG - ORGANIC") ~ 660002,
                                    str_detect(comm, "WATERMELON-ORGANIC") ~ 100082,
                                    str_detect(comm, "WHEAT-ORGANIC") ~ 291392
                                    ))

kern_2018$new_comm_code[is.na(kern_2018$new_comm_code)] <- kern_2018$comm_code[is.na(kern_2018$new_comm_code)]


kern_2019 <- read_sf(here("kern2019"), layer = "kern2019") %>% 
clean_names() %>% 
   mutate(landuse = case_when(comm_code == 66000 ~ 'fallow',
                             TRUE ~ 'cropland')) %>% 
   mutate(new_comm_code = case_when(str_detect(comm, "ALMOND-ORGANIC") ~ 30012,
                                    str_detect(comm, "APPLE-ORGANIC") ~ 40012,
                                    str_detect(comm, "APRICOT-ORGANIC") ~ 40012,
                                    str_detect(comm, "ARUGULA-ORGANIC") ~ 130562,
                                    str_detect(comm, "BEAN SUCCULENT-ORGANIC") ~ 150032,
                                    str_detect(comm, "BEET-ORGANIC") ~ 291092,
                                    str_detect(comm, "BLUEBERRY-ORGAN") ~ 10092,
                                    str_detect(comm, "BROCCOLI-ORGANI") ~ 130052,
                                    str_detect(comm, "CABBAGE-ORGANIC") ~ 130072,
                                    str_detect(comm, "CARROT-ORGANIC") ~ 291112,
                                    str_detect(comm, "CAULIFLOWER-ORGANIC") ~ 130082,
                                    str_detect(comm, "CHERRY-ORGANIC") ~ 50022,
                                    str_detect(comm, "CILANTRO-ORGANI") ~ 135012,
                                    str_detect(comm, "COLLARD-ORGANIC") ~ 130092,
                                    str_detect(comm, "CORN, HUMAN CON-ORGANIC") ~ 291192,
                                    str_detect(comm, "CUCUMBER-ORGANI") ~ 100102,
                                    str_detect(comm, "DILL-ORGANIC") ~ 80152,
                                    str_detect(comm, "EGGPLANT-ORGANI") ~ 110012,
                                    str_detect(comm, "FENNEL-ORGANIC") ~ 280082,
                                    str_detect(comm, "GARLIC-ORGANIC") ~ 140072,
                                    str_detect(comm, "GRAPE-ORGANIC") ~ 291412,
                                    str_detect(comm, "GRAPE, WINE-ORGANIC") ~ 291432,
                                    str_detect(comm, "GRAPEFRUIT-ORGANIC") ~ 20022,
                                    str_detect(comm, "KALE-ORGANIC") ~ 130112,
                                    str_detect(comm, "KOHLRABI-ORGANI") ~ 130122,
                                    str_detect(comm, "CHERRY-ORGANIC") ~ 50022,
                                    str_detect(comm, "LEMON-ORGANIC") ~ 20042,
                                    str_detect(comm, "LETTUCE HEAD-ORGANIC") ~ 130452,
                                    str_detect(comm, "MELON-ORGANIC") ~ 291222,
                                    str_detect(comm, "MINT-ORGANIC") ~ 280122,
                                    str_detect(comm, "OAT-ORGANIC") ~ 291252,
                                    str_detect(comm, "OKRA-ORGANIC") ~ 150152,
                                    str_detect(comm, "ONION DRY ETC-ORGANIC") ~ 140112,
                                    str_detect(comm, "ORANGE-ORGANIC") ~ 20062,
                                    str_detect(comm, "PARSLEY-ORGANIC") ~ 130222,
                                    str_detect(comm, "PEAS-ORGANIC") ~ 291272,
                                    str_detect(comm, "PEPPER FRUITNG-ORGANIC") ~ 110032,
                                    str_detect(comm, "PEPPER SPICE-ORGANIC") ~ 80502,
                                    str_detect(comm, "PERSIMMON-ORGANIC") ~ 60122,
                                    str_detect(comm, "POMEGRANATE-ORGANIC") ~ 60152,
                                    str_detect(comm, "POTATO-ORGANIC") ~ 140132,
                                    str_detect(comm, "RADISH-ORGANIC") ~ 140142,
                                    str_detect(comm, "SAFFLOWER-ORGANIC") ~ 291292,
                                    str_detect(comm, "SPINACH-ORGANIC") ~ 130242,
                                    str_detect(comm, "SQUASH-ORGANIC") ~ 100122,
                                    str_detect(comm, "SQUASH, WINTER-ORGANIC") ~ 100142,
                                    str_detect(comm, "SWISS CHARD-ORGANIC") ~ 130252,
                                    str_detect(comm, "TANGELO-ORGANIC") ~ 20072,
                                    str_detect(comm, "TANGERINE-ORGANIC") ~ 20082,
                                    str_detect(comm, "TOMATO PROCESS-ORGANIC") ~ 291362,
                                    str_detect(comm, "TOMATO-ORGANIC") ~ 110052,
                                    str_detect(comm, "TURNIP-ORGANIC") ~ 291372,
                                    str_detect(comm, "UNCULTIVATED AG - ORGANIC") ~ 660002,
                                    str_detect(comm, "WATERMELON-ORGANIC") ~ 100082,
                                    str_detect(comm, "WHEAT-ORGANIC") ~ 291392
                                    ))

kern_2019$new_comm_code[is.na(kern_2019$new_comm_code)] <- kern_2019$comm_code[is.na(kern_2019$new_comm_code)]
kern_2019$comm_code <- as.character(kern_2019$comm_code)
kern_2019$new_comm_code <- as.character(kern_2019$new_comm_code)

```


### Exporting as csv or shp for GEE 
```{r}
## Export the new dfs  as csvs 
# write.csv(kern_2017,file ="kern2017new.csv", row.names =  FALSE, fileEncoding="UTF-16LE")
# write.csv(kern_2018,file ="kern2018new.csv", row.names =  FALSE, fileEncoding="UTF-16LE")
# write.csv(kern_2019,file ="kern2019new.csv", row.names =  FALSE, fileEncoding="UTF-16LE")

## Export the new dfs as shapefiles instead
kern_2017 <- st_transform(kern_2017, st_crs(kern_2016))
# st_crs(kern_2017) #to check Coordinate Reference System
kern_2018 <- st_transform(kern_2018, st_crs(kern_2016))
kern_2019 <- st_transform(kern_2019, st_crs(kern_2016))
ggplot() +
  geom_sf(data = kern_2017) +
  ggtitle("testing") # quick plot to check everything looks right 

## exporting as shps 
 # st_write(kern_2017,
 #          "kern2017new.shp", driver = "ESRI Shapefile")
 # st_write(kern_2018,
 #          "kern2018new.shp", driver = "ESRI Shapefile")
 # st_write(kern_2019,
 #          "kern2019new.shp", driver = "ESRI Shapefile")
 
 
```


### Read in the new csvs with the mean column (mean ndvi extracted from GEE: https://code.earthengine.google.com/0702d5f0c44fdbada073407474bd43b6)
```{r}
kern2017ndvi <- read.csv(here("kern2017ndvi","2017_kern_mean_ndvi.csv"))
kern2018ndvi <- read.csv(here("kern2018ndvi","2018_kern_mean_ndvi.csv"))
kern2019ndvi <- read.csv(here("kern2019ndvi","2019_kern_mean_ndvi.csv"))
```


## Read in Families csv to aggregate by "agroclass"
```{r}
famililes <- read.csv(here("Families_Abandonment.csv"))
```

## Apply a string function so that if, for example, comm = almond, agroclass = nuts
```{r}
# Merge on Comm 
merge_kern_2017 <- merge(kern_2017, famililes, by=c("comm"), 
                  all=TRUE) %>% 
  select(comm,dt_act,dt_inact,permit,permittee,species,agroclass)

merge_kern_2018 <- merge(kern_2018, famililes, by=c("comm"), 
                  all=TRUE) %>% 
  select(comm,dt_act,dt_inact,permit,permittee,species,agroclass)

merge_kern_2019 <- merge(kern_2019, famililes, by=c("comm"), 
                  all=TRUE) %>% 
  select(comm,dt_act,dt_inact,permit,permittee,species,agroclass)
 
```


## export the aggreated data frames
```{r}
## Export the new dfs as shapefiles 
merge_kern_2017 <- st_transform(merge_kern_2017, st_crs(kern_2016))
merge_kern_2018 <- st_transform(merge_kern_2018, st_crs(kern_2016))
merge_kern_2019 <- st_transform(merge_kern_2019, st_crs(kern_2016))


## exporting as shps 
 # st_write(merge_kern_2017,
 #          "mergekern2017", driver = "ESRI Shapefile")
 # st_write(merge_kern_2018,
 #          "mergekern2018", driver = "ESRI Shapefile")
 # st_write(merge_kern_2019,
 #          "mergekern2019", driver = "ESRI Shapefile")
```


```{r}
## grouping the newly merged kern county crop data by their assigned agroclass label and making sure the geometry is multi polygon to be able to load into GEE 
agg_2017 <- merge_kern_2017 %>%
  group_by(agroclass) %>%
  summarize(geometry = st_union(geometry)) %>% 
  filter(agroclass %in% c("Greenhouse", "FlowerCrop", "Barley", "Berries")) %>% 
  mutate(class = 1:n())


agg_2017_test <- aggregate(merge_kern_2017, list(merge_kern_2017$agroclass), function(x) x[1]) %>% ## taken from: https://stackoverflow.com/questions/42842635/aggregate-polygons-to-multipolygons-and-keep-data-frame
   mutate(class = 1:n())

 ## agg_2017 <- agg_2017[1:1,] ## attemping to reduce the frame to see if the classifier will run on a reduced dataset with just 2 rows of crops and their multipolygn dimentions 

agg_2018 <- merge_kern_2018 %>%
  group_by(agroclass) %>%
  summarize() %>% 
mutate(geometry = st_union(geometry))

agg_2019 <- merge_kern_2019 %>%
  group_by(agroclass) %>%
  summarize() %>% 
    mutate(geometry = st_union(geometry))

# making sure their coordinate reference system all match 
agg_2017 <- st_transform(agg_2017, st_crs(kern_2016))
agg_2017_test <- st_transform(agg_2017_test, st_crs(kern_2016))
agg_2018 <- st_transform(agg_2018, st_crs(kern_2016))
agg_2019 <- st_transform(agg_2019, st_crs(kern_2016))


```


```{r}
## export as shp files
# st_write(agg_2017,
#           "agg_2017_new_test_berries", driver = "ESRI Shapefile")
# st_write(agg_2017_test,
#           "agg_2017_new_testrun", driver = "ESRI Shapefile")
# st_write(agg_2018,
#           "agg_2018_new", driver = "ESRI Shapefile")
# st_write(agg_2019,
#           "agg_2019_new", driver = "ESRI Shapefile")
```

```{r}
aa <- count(merge_kern_2017, agroclass) %>% arrange(n) %>% head(n=60)

agg_2017 <- merge_kern_2017 %>%
  group_by(agroclass) %>%
  summarize(geometry = st_union(geometry)) %>% 
  filter(agroclass %in% c("Greenhouse", "FlowerCrop", "Barley", "Berries", "OrnamentalTree", "Seed", "Oats", "Pasture", "Rye", "Leguminous", "Ornamental" , "UncultivatedAg")) %>% 
  mutate(class = 1:n())

agg_2017 <- st_transform(agg_2017, st_crs(kern_2016))

 st_write(agg_2017,
           "agg_2017_new_test_ornamental", driver = "ESRI Shapefile")

```


```{r}
kern_2015union <- kern_2015 %>% st_union()
## write_sf(kern_2015u,"kern2015_union.shp")
```

## Filtering greater than or equal to 0.4 mean NDVI for kern 2015 field polygons 
```{r}
kern_2015_mean_NDVI <- read_csv(here("kern2015meanNDVI", "2015_kern_mean_ndvi.csv")) 

kern_2015_gte <- kern_2015_mean_NDVI %>% 
 mutate(classification = 
          case_when(mean >= 0.4 ~ "agriculture",
                    mean < 0.4 ~ "fallow"))

kern_2015_agriculture <- kern_2015_mean_NDVI %>% filter(mean >= 0.4)
kern_2015_fallow <- kern_2015_mean_NDVI %>% filter(mean < 0.4)

#write.csv(kern_2015_agriculture,file ="kern_2015_agriculture.csv", row.names =  FALSE)
#write.csv(kern_2015_fallow,file ="kern_2015_fallow.csv", row.names =  FALSE)
```

## Filtering greater than or equal to 0.4 mean NDVI for kern 2011 field polygons 
```{r}
kern_2011_mean_NDVI <- read_csv(here("kern2011meanNDVI", "2011_kern_mean_ndvi.csv")) 

kern_2011_gte <- kern_2011_mean_NDVI %>% 
 mutate(classification = 
          case_when(mean >= 0.4 ~ "agriculture",
                    mean < 0.4 ~ "fallow"))

kern_2011_gte <- st_transform(kern_2011_gte, st_crs(kern_2016))


kern_2011_agriculture <- kern_2011_gte %>% filter(mean >= 0.4)
kern_2011_fallow <- kern_2011_gte %>% filter(mean < 0.4)

write.csv(kern_2011_agriculture,file ="kern_2011_agriculture.csv", row.names =  FALSE)
write.csv(kern_2011_fallow,file ="kern_2011_fallow.csv", row.names =  FALSE)
```

```{r}
kern_2017_mean_NDVI <- read_csv(here("kern2017meanNDVI", "2017_kern_mean_ndvi.csv")) 

kern_2017_gte <- kern_2017_mean_NDVI %>% 
 mutate(classification = 
          case_when(mean >= 0.4 ~ "agriculture",
                    mean < 0.4 ~ "fallow"))
kern_2017_agriculture <- kern_2017_gte %>% filter(mean >= 0.4)
kern_2017_fallow <- kern_2017_gte %>% filter(mean < 0.4)

write.csv(kern_2017_agriculture,file ="kern_2017_agriculture.csv", row.names =  FALSE)
write.csv(kern_2017_fallow,file ="kern_2017_fallow.csv", row.names =  FALSE)
```

## l7l8 harmonized 2015 mean NDVI 
```{r}
kern_2015_mean_NDVI_l7l8<- read_csv(here("kern2015meanNDVIl7l8", "2015_kern_mean_ndvi_l7l8.csv")) 

kern_2015_gte_l7l8 <- kern_2015_mean_NDVI_l7l8 %>% 
 mutate(classification = 
          case_when(mean >= 0.4 ~ "agriculture",
                    mean < 0.4 ~ "fallow"))

kern_2015_agriculture_l7l8 <- kern_2015_gte_l7l8 %>% filter(mean >= 0.4)
kern_2015_fallow_l7l8 <- kern_2015_gte_l7l8 %>% filter(mean < 0.4)

write.csv(kern_2015_agriculture_l7l8,file ="kern_2015_agriculture_l7l8.csv", row.names =  FALSE)
write.csv(kern_2015_fallow_l7l8,file ="kern_2015_fallow_l7l8.csv", row.names =  FALSE)

```

